### 2022-03-07 paper/output/document/appendix.tex
spring cleaning xoxoxo

%
\begin{isabellebody}%
\setisabellecontext{appendix}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Appendix%
}
\isamarkuptrue%
%
\isamarkupsubsection{Alternate Definitions of a Maxim \label{maximmotive}%
}
\isamarkuptrue%
%
\isamarkupsubsubsection{Korsgaard's Act-Goal View%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
I adopt O'Niell's definition of a maxim, which builds on Korsgaard's weaker interpretation of 
a maxim as an act, goal pair. She interprets Kant's example meanings as having the form ``to-do-this-act-for-
the-sake-of-this-end,'' which could be formalized as a pair of an act and goal \citep{actingforareason}.
For example, under this view, one example maxim might be, ``Falsely promise to repay a loan in order
to get some easy cash.''

@@

One other reason to be concerned with Korsgaard's view is that an actionable maxim will necessarily
require some circumstances built-in because the agent will need to know when to act on the maxim. For example,
the falsely promising maxim bakes in the circumstances that the actor has access to lender, needs money, 
and that the lender will expect their money back. At an even more granular level, this maxim implicitly includes
a definition of a lender and of falsely promising, both of which are circumstantial. Given that all
maxims necessarily include some circumstances, O'Niell's view makes these implicit circumstances
explicit. This precision is a benefit; so long as my circumstances are not so finely grained that they
are uninterpretable, they render O'Niell's kind of maxims more precise than Korsgaard's form.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsubsection{Kitcher's View on Motives%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
A stronger view than O'Niell's is due to Patricia Kitcher. Kitcher begins with O'Niell's 
circumstance, act, goal view and expands it to include the motive for a maxim \citep{whatisamaxim}. 
This additional component is read as ``In circumstance C, I will do A in order to G because of M,'' 
where M may be ``duty'' or ``self-love.'' Kitcher argues that the inclusion of motive is necessary 
for the fullest, most general form of a maxim in order to capture Kant's idea that an action derives 
its moral worth from being done for the sake of duty itself. Under this view, the FUL would obligate maxims of the form 
``In circumstance C, I will do A in order to G because I can will that I and everyone else simultaneously
will do A in order to G in circumstance C.'' In other words, if Kant is correct in arguing that moral 
actions must be done from the motive of duty, the affirmative result of the FUL becomes 
the motive for a moral action.

@@

\isamarkupsubsection{Kroy's Formalization\label{kroydetails}%

@@

\isamarkupsubsubsection{Logical Background \label{sec:kroy_logical_background}%

@@

  Free variable:
    A = ($\lambda x. \_$)($i_1$ := False) \color{black}%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
In order to make this true, we'd have to require that everything is either obligatory or
prohibited somewhere, but this makes permissibility impossible, which is clearly undesirable.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsubsection{Kroy's formalization of the FUL \label{sec: kroy_ful}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
I now implement Kroy's formalization of the Formula of Universal Law. Recall that the FUL says
``act only in accordance with that maxim which you can at the same time will a universal law'' \citep{groundwork}.
Kroy interprets this to mean that if an action is permissible for a specific agent, then it must be permissible for everyone.
This formalizes the moral intuition prohibiting free-riding. According to the categorical imperative, 
no one is a moral exception.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ FUL{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}FUL\ {\isasymequiv}\ {\isasymforall}w\ A{\isachardot}\ {\isacharparenleft}{\isacharparenleft}{\isasymexists}p{\isacharcolon}{\isacharcolon}s{\isachardot}\ {\isacharparenleft}{\isacharparenleft}P\ {\isacharbraceleft}A\ p{\isacharbraceright}{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}\ \ {\isasymlongrightarrow}{\isacharparenleft}\ {\isacharparenleft}{\isasymforall}p{\isachardot}{\isacharparenleft}\ P\ {\isacharbraceleft}A\ p{\isacharbraceright}{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isacharparenright}\ {\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{If action $A$ is permissible for some person, then, for any person $p$, action $A$ must be 
permissible for $p$. The notion of ``permissible for'' 
is captured by the substitution of $x$ for $p$.%
}%
\begin{isamarkuptext}%
This formalization does not hold in DDL, the base logic. This means that Kroy's formalization
already passes one test, and that adding it as an axiom will strengthen the logic.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ FUL{\isacharcolon}\isanewline
\ \ \isakeyword{shows}\ FUL\isanewline
\ \ \isacommand{nitpick}\isamarkupfalse%
{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
\isanewline
%
\isamarkupcmt{\color{blue} Nitpick found a counterexample for card s = 2 and card i = 2:

@@

  Empty assignment\color{black}%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
This completes my implementation of Kroy's formalization of the first formulation of the 
categorical imperative. I defined new logical constructs to handle Kroy's logic, studied the differences
between DDL and Kr, implemented Kroy's formalization of the Formula of Universal Law, and showed 
that it is both non-trivial and consistent.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsubsection{Testing Kroy's Formalization%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
In this section, I use my testing framework to evaluate Kroy's formalization. I find that, while 
        the formalization is considerably
        stronger than the naive formalization, it still fails many of these tests. Some of these failures 
        are due to the differences between Kroy's logic and my logic mentioned in Section \ref{sec:kroy_logical_background}, but some 
        reveal philosophical problems with Kroy's interpretation of what the formula of universal law means.

@@

        Neither of these errors are obvious from Kroy's presentation of his formalization of 
        the categorical imperative. This example demonstrates the power of formalized ethics. Making
        Kroy's interpretation of the categorical imperative precise demonstrated a philosophical problem 
        with that interpretation.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsubsection{Metaethical Tests \label{sec:meta_tests_kroy}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
In addition to testing specific applications of the theory, I am also interested in 
        metaethical properties, as in the naive interpretation. First, I will test if permissiblility
        is possible under this formalization.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ permissible{\isacharcolon}\isanewline
\ \ \isakeyword{fixes}\ A\ w\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ A{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
\ \ \isacommand{nitpick}\isamarkupfalse%
\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}false{\isacharbrackright}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
\isanewline
%
\isamarkupcmt{\color{blue}Nitpick found a model for card i = 1:

@@

\isamarkupsubsubsection{Miscellaneous Tests \label{sec: misc_tests_kroy}%

@@

%:%24=5%:%
%:%28=7%:%
%:%32=9%:%
%:%44=11%:%
%:%45=12%:%
%:%46=13%:%
%:%47=14%:%
%:%48=15%:%
%:%49=16%:%
%:%50=17%:%
%:%51=18%:%
%:%52=19%:%
%:%53=20%:%
%:%54=21%:%
%:%55=22%:%
%:%56=23%:%
%:%57=24%:%
%:%58=25%:%
%:%59=26%:%
%:%60=27%:%
%:%61=28%:%
%:%62=29%:%
%:%63=30%:%
%:%64=31%:%
%:%65=32%:%
%:%66=33%:%
%:%75=36%:%
%:%87=38%:%
%:%88=39%:%
%:%89=40%:%
%:%90=41%:%
%:%91=42%:%
%:%92=43%:%
%:%93=44%:%
%:%94=45%:%
%:%95=46%:%
%:%96=47%:%
%:%97=48%:%
%:%98=49%:%
%:%99=50%:%
%:%100=51%:%
%:%101=52%:%
%:%102=53%:%
%:%103=54%:%
%:%104=55%:%
%:%105=56%:%
%:%106=57%:%
%:%107=58%:%
%:%108=59%:%
%:%109=60%:%
%:%110=61%:%
%:%145=90%:%
%:%157=92%:%
%:%158=93%:%
%:%159=94%:%
%:%160=95%:%
%:%161=96%:%
%:%170=98%:%
%:%182=100%:%
%:%183=101%:%
%:%185=103%:%
%:%186=103%:%
%:%187=103%:%
%:%190=105%:%
%:%191=106%:%
%:%192=107%:%
%:%193=108%:%
%:%194=109%:%
%:%195=110%:%

@@

%:%198=112%:%
%:%200=113%:%
%:%201=113%:%
%:%203=114%:%
%:%204=115%:%
%:%207=117%:%
%:%208=118%:%
%:%209=119%:%
%:%210=120%:%
%:%212=122%:%
%:%213=122%:%
%:%214=123%:%
%:%215=124%:%
%:%216=124%:%
%:%217=125%:%
%:%218=126%:%
%:%219=126%:%
%:%220=127%:%
%:%221=128%:%
%:%222=128%:%
%:%223=129%:%
%:%225=131%:%
%:%226=132%:%
%:%227=133%:%
%:%229=135%:%
%:%230=135%:%
%:%231=136%:%
%:%232=137%:%
%:%233=137%:%
%:%234=138%:%
%:%235=140%:%
%:%238=142%:%
%:%239=143%:%
%:%240=144%:%
%:%241=145%:%
%:%242=146%:%
%:%243=147%:%
%:%244=148%:%
%:%247=150%:%
%:%250=152%:%
%:%251=153%:%
%:%252=154%:%
%:%253=155%:%
%:%254=156%:%
%:%255=157%:%
%:%257=159%:%
%:%258=159%:%
%:%259=160%:%

@@

%:%261=162%:%
%:%262=162%:%
%:%264=162%:%
%:%268=162%:%
%:%269=162%:%
%:%271=163%:%
%:%272=164%:%
%:%273=165%:%
%:%274=166%:%
%:%284=168%:%
%:%285=169%:%
%:%286=170%:%
%:%287=171%:%
%:%288=172%:%
%:%289=173%:%
%:%290=174%:%
%:%291=175%:%
%:%292=176%:%
%:%293=177%:%
%:%295=179%:%
%:%296=179%:%
%:%297=180%:%

@@

%:%299=182%:%
%:%300=182%:%
%:%302=182%:%
%:%306=182%:%
%:%307=182%:%
%:%309=183%:%
%:%310=184%:%
%:%311=185%:%
%:%312=186%:%
%:%322=188%:%
%:%323=189%:%
%:%324=190%:%
%:%325=191%:%
%:%326=192%:%
%:%327=193%:%
%:%328=194%:%
%:%329=195%:%
%:%330=196%:%
%:%332=198%:%
%:%333=198%:%
%:%334=199%:%

@@

%:%336=201%:%
%:%337=201%:%
%:%339=201%:%
%:%343=201%:%
%:%344=201%:%
%:%346=202%:%
%:%347=203%:%
%:%348=204%:%
%:%349=205%:%
%:%359=207%:%
%:%360=208%:%
%:%382=234%:%
%:%394=236%:%
%:%395=237%:%
%:%396=238%:%
%:%397=239%:%
%:%398=240%:%
%:%400=243%:%
%:%401=243%:%
%:%403=244%:%
%:%404=245%:%
%:%405=246%:%
%:%408=248%:%
%:%409=249%:%
%:%411=251%:%
%:%412=251%:%

@@

%:%414=253%:%
%:%415=253%:%
%:%417=253%:%
%:%421=253%:%
%:%422=253%:%
%:%424=254%:%
%:%425=255%:%
%:%426=256%:%
%:%427=257%:%
%:%428=258%:%
%:%429=259%:%
%:%437=259%:%
%:%438=260%:%
%:%439=261%:%
%:%440=261%:%
%:%442=263%:%
%:%443=264%:%
%:%445=266%:%
%:%446=266%:%
%:%447=266%:%
%:%449=266%:%
%:%453=266%:%
%:%454=266%:%
%:%456=267%:%
%:%457=268%:%
%:%458=269%:%
%:%459=270%:%
%:%469=272%:%
%:%470=273%:%
%:%471=274%:%
%:%472=275%:%
%:%481=277%:%
%:%493=279%:%
%:%494=280%:%
%:%495=281%:%
%:%496=282%:%
%:%497=283%:%
%:%498=284%:%
%:%499=285%:%
%:%500=286%:%
%:%501=287%:%
%:%502=288%:%
%:%504=290%:%
%:%505=290%:%

@@

%:%507=292%:%
%:%508=292%:%
%:%510=292%:%
%:%514=292%:%
%:%524=294%:%
%:%528=296%:%
%:%529=297%:%
%:%530=298%:%
%:%532=300%:%
%:%533=300%:%
%:%535=301%:%
%:%536=302%:%
%:%537=303%:%
%:%538=304%:%
%:%539=305%:%
%:%540=306%:%
%:%541=307%:%
%:%542=307%:%
%:%543=308%:%
%:%544=309%:%
%:%545=309%:%
%:%546=310%:%
%:%549=311%:%
%:%553=311%:%
%:%554=311%:%
%:%556=312%:%
%:%557=313%:%
%:%567=315%:%
%:%568=316%:%
%:%569=317%:%
%:%570=318%:%
%:%571=319%:%
%:%572=320%:%
%:%573=321%:%
%:%574=322%:%
%:%575=323%:%
%:%576=324%:%
%:%577=325%:%
%:%578=326%:%
%:%579=327%:%
%:%580=328%:%
%:%581=329%:%
%:%582=330%:%
%:%583=331%:%
%:%584=332%:%
%:%588=334%:%
%:%589=335%:%

@@

%:%592=337%:%
%:%594=338%:%
%:%595=338%:%
%:%596=339%:%
%:%597=340%:%
%:%598=340%:%
%:%599=341%:%
%:%602=342%:%
%:%606=342%:%
%:%607=342%:%
%:%608=343%:%
%:%609=343%:%

@@

%:%611=344%:%
%:%612=345%:%
%:%613=345%:%
%:%614=345%:%
%:%615=346%:%
%:%625=348%:%
%:%626=349%:%
%:%627=350%:%
%:%628=351%:%
%:%632=353%:%
%:%636=355%:%
%:%637=356%:%
%:%638=357%:%
%:%642=359%:%
%:%643=360%:%
%:%645=362%:%
%:%646=362%:%
%:%659=383%:%
%:%660=384%:%
%:%661=384%:%
%:%663=385%:%
%:%664=386%:%
%:%665=387%:%
%:%666=388%:%
%:%667=389%:%
%:%668=390%:%
%:%669=390%:%
%:%671=391%:%
%:%672=392%:%
%:%673=392%:%
%:%674=393%:%
%:%675=394%:%
%:%676=394%:%
%:%678=395%:%
%:%679=396%:%
%:%682=398%:%
%:%683=399%:%
%:%685=401%:%
%:%686=401%:%

@@

%:%688=403%:%
%:%689=403%:%
%:%691=403%:%
%:%695=403%:%
%:%696=403%:%
%:%698=404%:%
%:%699=405%:%
%:%700=406%:%
%:%701=407%:%

>>>>

%
\begin{isabellebody}%
\setisabellecontext{appendix}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Appendix: Alternate Definitions of a Maxim \label{maximmotive}%
}
\isamarkuptrue%
%
\isamarkupsubsection{Korsgaard's Act-Goal View%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
I adopt O'Niell's definition of a maxim, which builds on Korsgaard's weaker interpretation of 
a maxim as an act, goal pair. She interprets Kant's example meanings as having the form ``to-do-this-act-for-
the-sake-of-this-end,'' which could be formalized as a pair of an act and goal \citep{actingforareason}.
For example, under this view, one example maxim might be, ``Falsely promise to repay a loan in order
to get some easy cash.''

@@

One other reason to be concerned with Korsgaard's view is that an actionable maxim will necessarily
require some circumstances built-in because the agent will need to know when to act on the maxim. For example,
the falsely promising maxim bakes in the circumstances that the actor has access to lender, needs money, 
and that the lender will expect their money back. At an even more granular level, this maxim implicitly includes
a definition of a lender and of falsely promising, both of which are circumstantial. Given that all
maxims necessarily include some circumstances, O'Niell's view makes these implicit circumstances
explicit. This precision is a benefit; so long as my circumstances are not so finely grained that they
are uninterpretable, they render O'Niell's kind of maxims more precise than Korsgaard's form.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Kitcher's View on Motives%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
A stronger view than O'Niell's is due to Patricia Kitcher. Kitcher begins with O'Niell's 
circumstance, act, goal view and expands it to include the motive for a maxim \citep{whatisamaxim}. 
This additional component is read as ``In circumstance C, I will do A in order to G because of M,'' 
where M may be ``duty'' or ``self-love.'' Kitcher argues that the inclusion of motive is necessary 
for the fullest, most general form of a maxim in order to capture Kant's idea that an action derives 
its moral worth from being done for the sake of duty itself. Under this view, the FUL would obligate maxims of the form 
``In circumstance C, I will do A in order to G because I can will that I and everyone else simultaneously
will do A in order to G in circumstance C.'' In other words, if Kant is correct in arguing that moral 
actions must be done from the motive of duty, the affirmative result of the FUL becomes 
the motive for a moral action.

@@

\isamarkupsection{Kroy's Formalization\label{kroydetails}%

@@

\isamarkupsubsection{Logical Background \label{sec:kroy_logical_background}%

@@

  Free variable:
    A = ($\lambda x. \_$)($i_1$ := False) \color{black}%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
In order to make this true, we'd have to require that everything is either obligatory or
prohibited somewhere, but this makes permissibility impossible, which is clearly undesirable.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimproof
%
\endisadelimproof
%
\isatagproof
%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Kroy's formalization of the FUL \label{sec: kroy_ful}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
I now implement Kroy's formalization of the Formula of Universal Law. Recall that the FUL says
``act only in accordance with that maxim which you can at the same time will a universal law'' \citep{groundwork}.
Kroy interprets this to mean that if an action is permissible for a specific agent, then it must be permissible for everyone.
This formalizes the moral intuition prohibiting free-riding. According to the categorical imperative, 
no one is a moral exception.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ FUL{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}FUL\ {\isasymequiv}\ {\isasymforall}w\ A{\isachardot}\ {\isacharparenleft}{\isacharparenleft}{\isasymexists}p{\isacharcolon}{\isacharcolon}s{\isachardot}\ {\isacharparenleft}{\isacharparenleft}P\ {\isacharbraceleft}A\ p{\isacharbraceright}{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}\ \ {\isasymlongrightarrow}{\isacharparenleft}\ {\isacharparenleft}{\isasymforall}p{\isachardot}{\isacharparenleft}\ P\ {\isacharbraceleft}A\ p{\isacharbraceright}{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isacharparenright}\ {\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{If action $A$ is permissible for some person, then, for any person $p$, action $A$ must be 
permissible for $p$. The notion of ``permissible for'' 
is captured by the substitution of $x$ for $p$.%
}%
\begin{isamarkuptext}%
This formalization does not hold in DDL, the base logic. This means that Kroy's formalization
already passes one test, and that adding it as an axiom will strengthen the logic.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ FUL{\isacharcolon}\isanewline
\ \ \isakeyword{shows}\ FUL\isanewline
\ \ \isacommand{nitpick}\isamarkupfalse%
{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
\isanewline
%
\isamarkupcmt{\color{blue} Nitpick found a counterexample for card s = 2 and card i = 2:

@@

  Empty assignment\color{black}%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
This completes my implementation of Kroy's formalization of the first formulation of the 
categorical imperative. I defined new logical constructs to handle Kroy's logic, studied the differences
between DDL and Kr, implemented Kroy's formalization of the Formula of Universal Law, and showed 
that it is both non-trivial and consistent.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Testing Kroy's Formalization%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
In this section, I use my testing framework to evaluate Kroy's formalization. I find that, while 
        the formalization is considerably
        stronger than the naive formalization, it still fails many of these tests. Some of these failures 
        are due to the differences between Kroy's logic and my logic mentioned in Section \ref{sec:kroy_logical_background}, but some 
        reveal philosophical problems with Kroy's interpretation of what the formula of universal law means.

@@

        Neither of these errors are obvious from Kroy's presentation of his formalization of 
        the categorical imperative. This example demonstrates the power of formalized ethics. Making
        Kroy's interpretation of the categorical imperative precise demonstrated a philosophical problem 
        with that interpretation.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Metaethical Tests \label{sec:meta_tests_kroy}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
In addition to testing specific applications of the theory, I am also interested in 
        metaethical properties, as in the naive interpretation. First, I will test if permissiblility
        is possible under this formalization.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ permissible{\isacharcolon}\isanewline
\ \ \isakeyword{fixes}\ A\ w\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}{\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}{\isacharparenright}{\isacharparenright}\ \isactrlbold {\isasymand}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}\ A{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
\ \ \isacommand{nitpick}\isamarkupfalse%
\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharcomma}\ falsify{\isacharequal}false{\isacharbrackright}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
\isanewline
%
\isamarkupcmt{\color{blue}Nitpick found a model for card i = 1:

@@

\isamarkupsubsection{Miscellaneous Tests \label{sec: misc_tests_kroy}%

@@

%:%24=6%:%
%:%28=8%:%
%:%40=10%:%
%:%41=11%:%
%:%42=12%:%
%:%43=13%:%
%:%44=14%:%
%:%45=15%:%
%:%46=16%:%
%:%47=17%:%
%:%48=18%:%
%:%49=19%:%
%:%50=20%:%
%:%51=21%:%
%:%52=22%:%
%:%53=23%:%
%:%54=24%:%
%:%55=25%:%
%:%56=26%:%
%:%57=27%:%
%:%58=28%:%
%:%59=29%:%
%:%60=30%:%
%:%61=31%:%
%:%62=32%:%
%:%71=35%:%
%:%83=37%:%
%:%84=38%:%
%:%85=39%:%
%:%86=40%:%
%:%87=41%:%
%:%88=42%:%
%:%89=43%:%
%:%90=44%:%
%:%91=45%:%
%:%92=46%:%
%:%93=47%:%
%:%94=48%:%
%:%95=49%:%
%:%96=50%:%
%:%97=51%:%
%:%98=52%:%
%:%99=53%:%
%:%100=54%:%
%:%101=55%:%
%:%102=56%:%
%:%103=57%:%
%:%104=58%:%
%:%105=59%:%
%:%106=60%:%
%:%141=89%:%
%:%153=91%:%
%:%154=92%:%
%:%155=93%:%
%:%156=94%:%
%:%157=95%:%
%:%166=97%:%
%:%178=99%:%
%:%179=100%:%
%:%181=102%:%
%:%182=102%:%
%:%183=102%:%
%:%186=104%:%
%:%187=105%:%
%:%188=106%:%
%:%189=107%:%
%:%190=108%:%
%:%191=109%:%
%:%193=111%:%
%:%194=111%:%
%:%196=112%:%

@@

%:%199=113%:%
%:%200=114%:%
%:%203=116%:%
%:%204=117%:%
%:%205=118%:%
%:%206=119%:%
%:%208=121%:%
%:%209=121%:%
%:%210=122%:%
%:%211=123%:%
%:%212=123%:%
%:%213=124%:%
%:%214=125%:%
%:%215=125%:%
%:%216=126%:%
%:%217=127%:%
%:%218=127%:%
%:%219=128%:%
%:%221=130%:%
%:%222=131%:%
%:%223=132%:%
%:%225=134%:%
%:%226=134%:%
%:%227=135%:%
%:%228=136%:%
%:%229=136%:%
%:%230=137%:%
%:%231=139%:%
%:%234=141%:%
%:%235=142%:%
%:%236=143%:%
%:%237=144%:%
%:%238=145%:%
%:%239=146%:%
%:%240=147%:%
%:%243=149%:%
%:%246=151%:%
%:%247=152%:%
%:%248=153%:%
%:%249=154%:%
%:%250=155%:%
%:%251=156%:%
%:%253=158%:%
%:%254=158%:%
%:%255=159%:%
%:%256=160%:%
%:%257=161%:%
%:%258=161%:%

@@

%:%264=161%:%
%:%265=161%:%
%:%267=162%:%
%:%268=163%:%
%:%269=164%:%
%:%270=165%:%
%:%280=167%:%
%:%281=168%:%
%:%282=169%:%
%:%283=170%:%
%:%284=171%:%
%:%285=172%:%
%:%286=173%:%
%:%287=174%:%
%:%288=175%:%
%:%289=176%:%
%:%291=178%:%
%:%292=178%:%
%:%293=179%:%
%:%294=180%:%
%:%295=181%:%
%:%296=181%:%

@@

%:%302=181%:%
%:%303=181%:%
%:%305=182%:%
%:%306=183%:%
%:%307=184%:%
%:%308=185%:%
%:%318=187%:%
%:%319=188%:%
%:%320=189%:%
%:%321=190%:%
%:%322=191%:%
%:%323=192%:%
%:%324=193%:%
%:%325=194%:%
%:%326=195%:%
%:%328=197%:%
%:%329=197%:%
%:%330=198%:%
%:%331=199%:%
%:%332=200%:%
%:%333=200%:%

@@

%:%339=200%:%
%:%340=200%:%
%:%342=201%:%
%:%343=202%:%
%:%344=203%:%
%:%345=204%:%
%:%355=206%:%
%:%356=207%:%
%:%378=233%:%
%:%390=235%:%
%:%391=236%:%
%:%392=237%:%
%:%393=238%:%
%:%394=239%:%
%:%396=242%:%
%:%397=242%:%
%:%399=243%:%
%:%400=244%:%
%:%401=245%:%
%:%404=247%:%
%:%405=248%:%
%:%407=250%:%
%:%408=250%:%
%:%409=251%:%
%:%410=252%:%
%:%411=252%:%

@@

%:%417=252%:%
%:%418=252%:%
%:%420=253%:%
%:%421=254%:%
%:%422=255%:%
%:%423=256%:%
%:%424=257%:%
%:%425=258%:%
%:%433=258%:%
%:%434=259%:%
%:%435=260%:%
%:%436=260%:%
%:%438=262%:%
%:%439=263%:%
%:%441=265%:%
%:%442=265%:%
%:%443=265%:%
%:%445=265%:%
%:%449=265%:%
%:%450=265%:%
%:%452=266%:%
%:%453=267%:%
%:%454=268%:%
%:%455=269%:%
%:%465=271%:%
%:%466=272%:%
%:%467=273%:%
%:%468=274%:%
%:%477=276%:%
%:%489=278%:%
%:%490=279%:%
%:%491=280%:%
%:%492=281%:%
%:%493=282%:%
%:%494=283%:%
%:%495=284%:%
%:%496=285%:%
%:%497=286%:%
%:%498=287%:%
%:%500=289%:%
%:%501=289%:%
%:%502=290%:%
%:%503=291%:%
%:%504=291%:%

@@

%:%510=291%:%
%:%520=293%:%
%:%524=295%:%
%:%525=296%:%
%:%526=297%:%
%:%528=299%:%
%:%529=299%:%
%:%531=300%:%
%:%532=301%:%
%:%533=302%:%
%:%534=303%:%
%:%535=304%:%
%:%536=305%:%
%:%537=306%:%
%:%538=306%:%
%:%539=307%:%
%:%540=308%:%
%:%541=308%:%
%:%542=309%:%
%:%545=310%:%
%:%549=310%:%
%:%550=310%:%
%:%552=311%:%
%:%553=312%:%
%:%563=314%:%
%:%564=315%:%
%:%565=316%:%
%:%566=317%:%
%:%567=318%:%
%:%568=319%:%
%:%569=320%:%
%:%570=321%:%
%:%571=322%:%
%:%572=323%:%
%:%573=324%:%
%:%574=325%:%
%:%575=326%:%
%:%576=327%:%
%:%577=328%:%
%:%578=329%:%
%:%579=330%:%
%:%580=331%:%
%:%584=333%:%
%:%585=334%:%
%:%587=336%:%
%:%588=336%:%
%:%590=337%:%

@@

%:%592=338%:%
%:%593=339%:%
%:%594=339%:%
%:%595=340%:%
%:%598=341%:%
%:%602=341%:%
%:%603=341%:%
%:%604=342%:%
%:%605=342%:%
%:%606=343%:%
%:%607=343%:%
%:%608=344%:%
%:%609=344%:%

@@

%:%611=345%:%
%:%621=347%:%
%:%622=348%:%
%:%623=349%:%
%:%624=350%:%
%:%628=352%:%
%:%632=354%:%
%:%633=355%:%
%:%634=356%:%
%:%638=358%:%
%:%639=359%:%
%:%641=361%:%
%:%642=361%:%
%:%655=382%:%
%:%656=383%:%
%:%657=383%:%
%:%659=384%:%
%:%660=385%:%
%:%661=386%:%
%:%662=387%:%
%:%663=388%:%
%:%664=389%:%
%:%665=389%:%
%:%667=390%:%
%:%668=391%:%
%:%669=391%:%
%:%670=392%:%
%:%671=393%:%
%:%672=393%:%
%:%674=394%:%
%:%675=395%:%
%:%678=397%:%
%:%679=398%:%
%:%681=400%:%
%:%682=400%:%
%:%683=401%:%
%:%684=402%:%
%:%685=402%:%

@@

%:%691=402%:%
%:%692=402%:%
%:%694=403%:%
%:%695=404%:%
%:%696=405%:%
%:%697=406%:%
%:%698=407%:%
%:%699=408%:%
%:%700=409%:%
%:%710=411%:%
